Self Regulation Ontology Retest Analyses

### 2018-04-06 code/SRO_Retest_Analyses.Rmd
completing draft

Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)

```{r}
rel_comp = rel_comp %>%
  mutate(retest_reliability_ft = 0.5*log((1+retest_reliability)/(1-retest_reliability))) %>%
  filter(is.finite(retest_reliability_ft)==TRUE)

m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability_ft))
m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability_ft))
n1 = nrow(rel_comp %>% filter(task == "task"))
n2 = nrow(rel_comp %>% filter(task == "survey"))
var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability_ft))
var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability_ft))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_lit = abs(m1-m2)/sd_pooled
d_lit
```

`Add column for turk vs lab study`

The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size (for Fisher transformed reliability estimates).

@@

@@

boot_comp = boot_comp %>%
  mutate(task=ifelse(grepl("survey", dv), "task", "survey"),
         icc_ft = 0.5*log((1+icc)/(1-icc)))

m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc_ft))
m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc_ft))
n1 = nrow(boot_comp %>% filter(task == "task"))
n2 = nrow(boot_comp %>% filter(task == "survey"))
var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc_ft))
var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc_ft))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_boot = abs(m1-m2)/sd_pooled
d_boot
```

Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results.

This plot (weakly) supports that point that our results diverge most from studies with smaller sample sizes.

```{r}
rel_comp = rel_comp %>%
  mutate(diff_sq = abs(mean_icc - retest_reliability))

rel_comp %>%
  ggplot(aes(sample_size,diff_sq, color=task))+
  geom_point()+
  #exponential decay (linearized by taking logs of both sides)
  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
  theme_bw()+
  theme(legend.title = element_blank())
```

But as the plot suggests these are not significant effects overall.

```{r}
summary(lmer(diff_sq ~ sample_size*task + (1|dv), rel_comp))
```

```{r}
with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability, method="spearman"))
```

```{r}
with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability, method="spearman"))
```

>>>>

I used to compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature) but removed this analysis because   
1. the estimates in the literature are not all the same statistic
2. from our data I was only using ICC's
3. I was sampling from our bootstrapped results as many datapoints for each measure as there are in the literature but that didn't seem like the best way to make use of our data to make it comparable to the literature.

Despite these problems the main result was that the effect size was much larger in our dataset compared to the literature but given the problems I think the sampling analyses below are more informative than this.

We also checked whether our results diverge most from studies with smaller sample sizes. Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results. But this was a weak result because most of the studies in the literature have smaller sample sizes and you see both small and large deviations for these studies (these were not significant either).

@@

lit_emp_cor = function(){

@@

  #check if cbind is ok
  # sum(boot_comp$dv == rel_comp$dv)
  #cbinding pearson because that is the most common metric in the lit
  rel_comp = cbind(rel_comp, boot_comp$pearson)
  #rename new column
  names(rel_comp)[which(names(rel_comp) == "boot_comp$pearson")] = "pearson"

  out = data.frame(task = NA, survey = NA)

  out$task = with(rel_comp %>% filter(task == "task"), cor(pearson, retest_reliability))

  out$survey = with(rel_comp %>% filter(task == "survey"), cor(pearson, retest_reliability))

  rel_comp = rel_comp[,-16]

lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/lit_emp_cor_out.csv')

summary(lit_emp_cor_out)
